The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-15 article.tex
EOD

From an alignment, we run a Bayesian analysis and create a posterior, 
using the phylogetic tool BEAST2 \cite{beast2} using the 
pirouette (\cite{pirouette}) package. As our site model, we assume a Jukes-Cantor 
nucleotide substitution model, as we used that in the simulation of the alignment.
For our clock model, we assume a strict clock with the same fixed rate as 
used in the simulation of the alignment. The tree prior assumed is the BD model, 
as this simplification is the goal of this research. 
Additionally, we assume a MRCA prior with a normal distribution
with a mean of the crown age, and a standard deviation of 0.001 time units. 0.001
time units equates to 1000 years, which is the same resolution as which the
alignment is created. After discarding a burn-in of 10\%, the MCMC algorithm must 
result in an effective sample size (ESS) of the posterior of at least 200 
to have a strong enough inference (\cite{beastbook}). The MCMC sampling interval is 
chosen in such a way that this is the case for all simulations. For simulations
with an ESS below 200, their MCMC sampling interval is doubled up until
the ESS exceeds 200.

>>>>

From an alignment, we run a Bayesian analysis and create a posterior, 
using the phylogetic tool BEAST2 \cite{beast2} using the 
pirouette (\cite{pirouette}) package. As our site model, we assume a Jukes-Cantor 
nucleotide substitution model, as we used that in the simulation of the alignment.
For our clock model, we assume a strict clock with the same fixed rate as 
used in the simulation of the alignment. The tree prior assumed is the BD model, 
as this simplification is the goal of this research. 
Additionally, we assume a MRCA prior with a normal distribution
with a mean of the crown age, and a standard deviation of 0.001 time units. 0.001
time units equates to 1000 years, which is the same resolution as which the
alignment is created. The MCMC chain is run to generate 1100 states,
of which the first 10\% (also called the 'burn-in') is removed. Of the remaining
1000 MCMC states, the effective sample size (ESS) of the posterior must at least be 200
for a strong enough inference (\cite{beastbook}). The MCMC sampling interval is 
chosen in such a way that this is the case for all simulations. For simulations
with an ESS below 200, their MCMC sampling interval is doubled up until
the ESS exceeds 200.
